\documentstyle[12pt]{article}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{2.5cm}
\addtolength{\oddsidemargin}{-.75in}
\addtolength{\evensidemargin}{-.75in}
\addtolength{\textwidth}{.5in}
\begin{document}

%\vskip 1 in
\centerline{EVIDENCE OF PERFORMANCE}
%\centerline{(compressed format)}
\bigskip
\centerline{YEAR: \underbar{2016}}
\bigskip
\noindent Name: \underbar {David C. Collins }
\hbox{\ \ \ \ \ \ \ \
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ }
Rank: \underbar
{Assistant Professor }

%\bigskip
\vskip 20pt

\noindent A. YOUR MOST SIGNIFICANT CONTRIBUTIONS FOR THIS YEAR.
Please select from this document what you consider were your most
significant contributions in each of the areas of teaching, research
and service. PLEASE LIST THEM IN BULLET FORM AND ON A SINGLE PAGE.
If there is something important that you would like to mention which
lies outside these categories, please
place it in a category named ``Other'' at the bottom of this page. \\ \\

\noindent
Teaching:

\begin{itemize}
\item 4419/5418, Extragalactic Astronomy (Spring) and
\item 4341/5342, Hydrodynamics and Plasma for Astrophysics.  
\item Three PhD students, one Masters student, one undergraduate
\end{itemize}

%\vskip 100pt

\noindent
Research:

\begin{itemize}
\item Two funded grants, \$100k/year as PI and \$150k/year as Co-PI, both for 3
years.
\item Four papers.  
\item Three presentations from myself at conferences, four from
graduate students.
\end{itemize}

\noindent
Service:

\begin{itemize}
\item Qual committee (writing, grading, proctoring both quals in 2016)
\item Web committee (Chair)
\item Saturday Morning Physics
\end{itemize}



\newpage

\noindent B. PAPERS PUBLISHED THIS YEAR. Please list by citation all
papers of which you were an author that appeared during 2016.
(Designate whether refereed, conference proceeding, abstract etc.)
\bigskip

``Matching dust
emission structures and magnetic field in high-latitude cloud L1642: comparing
Herschel and Planck maps,''
Malinen, J.; Montier, L.; Montillaud, J.; Juvela, M.; Ristorcelli, I.; Clark, S.
E.; Bern\'e, O.; Bernard, J.-Ph.; Pelkonen, V.-M.; Collins, D. C. Monthly
Notices of the Royal Astronomical Society, 2016, 460, 1934

``GMC Collisions as Triggers of Star Formation. II. 3D Turbulent, Magnetized
Simulations'' Wu, B., Tan, J. C., Nakamura, F., Van Loo, S., Christie, D.,
Collins, D. C., ApJ, 20117, 835, 137

``The Razor’s Edge of Collapse: The Transition Point from Lognormal to Power-Law
Distributions in Molecular Clouds,'' Burkhart, B., Stalpes, K., Collins, D. C.,
ApJ, 2017, 834,1

\noindent C. PAPERS IN PRESS. Please list by citation all such
papers that were accepted but did not appear during 2016.
\bigskip


\noindent D. PAPERS SUBMITTED. Please list all papers that were
submitted by you but were not yet accepted during 2016.
\bigskip

``Length Scales and
Turbulent Properties of Magnetic Fields in Simulated Galaxy Clusters,'' Egan, O’Shea, Hallman, Burns, Xu, Collins, Li, Norman  submitted
to ApJ, arxiv 1601.05083
\bigskip

\noindent E. INDIVIDUAL TALKS. Please list all conference, symposia,
colloquia, seminar and other individual talks that you gave during
2016.  (Designate invited talks.)
\bigskip
%

``What’s the Deal with Dark Matter?'' July 18, 2016, and informal presentation
 at the Mag Lab for the participants in the \emph{Research Experience for
Teachers} program.

``Magnetic and Density Statistics in Collapsing Molecular Clouds Cores with
MHD,'' {\it Star Formation, Magnetic Fields, Diffuse Matter in the Galaxy}, University
of Wisconsin, Madison,
Wisconsin, May 25, 2016

``Astrophysical Turbulence: Nuclear Flame Propagation with Magnetic Fields,''
{\it Complex Interfaces in Geophysical and Astrophysical Fluid Dynamics}, April 29,
2016, FSU

``Magnetic Fields in Collapsing Molecular Clouds'' {\it From Stars to Massive
Stars},
University of Florida, Gainesville, FL April 6, 2016

``Line of Sight Contamination vs.  Virial Parameters,'' 
{\it Florida Star \& Planet Formation Days}, University of Florida, March 20,
2016
\bigskip
\noindent F. GRANT FUNDING. Please indicate your research funding
for 2016. Include any submitted  (even if not funded) or pending
proposals.
\bigskip
%

\emph{FUNDED}
\medskip

Collins, David C. (Co-PI), \& Huffenberger, Kevin (PI). (Feb 2017–Feb 2020).
``Modeling CMB Polarization Foregrounds and their Isotropy Violation.'' Funded
by National Aeronautics \& Space Administration. (NNX17AF87G). Total award to
date \$156,861. 

Collins, David C. (PI). (Sep 2016–Aug 2019). ``A Study of Magnetic Fields
in the Formation of Molecular Clouds and Stars.'' Funded by National
Science Foundation. (1616026). Total award \$100,544. 

``Tracking the Assembly History of Star Formation through Clouds, Filaments, and
Cores: Phase I.'' XSEDE computational resources.  Awarded 1.6 million CPU hours,
in kind value of \$50,000

\medskip
\emph{SUBMITTED, NOT FUNDED}
\medskip

``Magnetized Star Formation From the Big Bang to the Present, '' Cottrell
Scholars Award

``CAREER: Magnetizing the Universe.'' NSF CAREER award

``Magnetic Fields in Type Ia Supernovae,'' NASA theory program, with P.
H\"oflich.


``Tracking the Assembly History of Star Formation through Clouds, Filaments, and
Cores,'' NASA Theory program

\medskip
\emph{PENDING} 
\medskip

``Turbulence and Isotropy-Violation in Galactic Foregrounds to the
Cosmic Microwave Background'' NSF Astrophysics

``Signatures of Type Ia Supernovae Explosions,
New Physics, and Cosmology,'' NSF Astrophysics. 

\medskip
\noindent G. DEPARTMENTAL COMMITTEE SERVICE. Please list all
departmental committees on which you served during 2016.  Also
please indicate your committee assignment for this (spring)
semester.
\bigskip
\begin{itemize}
\item Qual committee (writing, grading, proctoring both quals in 2016)
\item Web committee (Chair)
\item Saturday Morning Physics
\end{itemize}
This will remain the same in Spring 2017.



\noindent H. UNIVERSITY AND SUS SERVICE. Please list all University
and SUS committees, task forces, and governing bodies on which you
served during 2016.
\bigskip
%

\noindent I. INTERNATIONAL, NATIONAL, AND REGIONAL  SERVICE. Please
list all international, national, and regional bodies on which you
served, together with any reviewing activities (journals,
proposals), during 2016.
\bigskip

Peer review for two journal articles, one for the Astrophysical Journal, the
other for Montly Notices of the Royal Astronomical Society.

\noindent J. OFFICES HELD. Please list all offices in organizations
related to your activity as a professional faculty member held by
you during 2016.
\bigskip

\noindent K. HONORS RECEIVED. Please list all professional honors
received by you during 2016.
\bigskip

\noindent L. GRADUATE DEGREES AWARDED. Please list all graduate
students who received degrees under your direction during 2016.
\bigskip


\noindent M. GRADUATE STUDENT DIRECTION. Please list all graduate
students whose work you directed during 2016 but who did not receive
degrees.
\bigskip

I continued advising the PhD of Dan K. Le, Kye Stalpes, 

I also continued advising Boyan Hristov, who is formally a FAMU graduate student
working with Charles Weatherford, but his practical thesis supervision is with
myself and Peter H\"oeflich.

I began working with Kye Stalpes, a PhD student, and Luz Jimenez, a Masters
student in the Bridge program.

I lost Damien Dennis to the Qual this year. 

I have been working with Corey Brummel-Smith, an undergraduate, who has been
extremely productive.   

\noindent N. GRADUATE STUDENT COMMITTEES. Please list all graduate
students on whose supervisory committees you served but for whom you
were not Major Professor during 2016.
\bigskip

Vincent Lakey, John Parker

\noindent O. UNDERGRADUATE SUPERVISION. Please list all
undergraduate students whose research activities you directed during
2016.
\bigskip

\begin{itemize}
\item Corey Brummel-Smith
\end{itemize}

\noindent P. CLASSES TAUGHT. Please list all classes you taught
during 2016 and what you are teaching this semester.  Include the
number of students in each class.
\bigskip
\begin{itemize}
\item 4419/5418, Extragalactic Astronomy (Spring 2016, Spring 2017) and
\item 4341/5342, Hydrodynamics and Plasma for Astrophysics.   (Fall 20160
\end{itemize}

\noindent Q. DIS SUPERVISION. Please list all DIS (Directed
Individual Study) students you directed during 2016.
\bigskip

\noindent R. OUTREACH ACTIVITIES. Please list all outreach
activities that you have participated in during 2016.
\bigskip

\begin{itemize}
\item Ask a Scientist (on 5 occasions)
\end{itemize}

\noindent S. OTHER ITEMS. Please detail any other items that you
feel will help give an adequate picture of your performance during
2016.
\bigskip

\noindent T.  SPOT EVALUATIONS. Please attach a copy of all student
evaluation SPCI form summary pages for your teaching during 2016.


\end{document}



