\documentstyle[12pt]{article}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{2.5cm}
\addtolength{\oddsidemargin}{-.75in}
\addtolength{\evensidemargin}{-.75in}
\addtolength{\textwidth}{.5in}
\begin{document}

%\vskip 1 in
\centerline{EVIDENCE OF PERFORMANCE}
%\centerline{(compressed format)}
\bigskip
\centerline{YEAR: \underbar{2018}}
\bigskip
\noindent Name: \underbar {David C. Collins }
\hbox{\ \ \ \ \ \ \ \
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ }
Rank: \underbar
{Assistant Professor }

%\bigskip
\vskip 20pt

\noindent A. YOUR MOST SIGNIFICANT CONTRIBUTIONS FOR THIS YEAR.
Please select from this document what you consider were your most
significant contributions in each of the areas of teaching, research
and service. PLEASE LIST THEM IN BULLET FORM AND ON A SINGLE PAGE.
If there is something important that you would like to mention which
lies outside these categories, please
place it in a category named ``Other'' at the bottom of this page. \\ \\

\noindent
Teaching:

\begin{itemize}
\item AST-4419/AST 5418, Extragalactic Astronomy (Spring) 
\item AST-4341/AST-5342, Hydrodynamcis for Astrophysics (Fall)
\item AST 5219/AST 4218 Astro Seminar (Spring)
\item Four PhD students, two undergraduate, one postdoc.
\item One PhD student graduated, became postdoc.
\end{itemize}

%\vskip 100pt

\noindent
Research:

\begin{itemize}
    \item Three papers accepted, one submitted
    \item Five invited presentations
\end{itemize}

%\vskip 100pt

\noindent
Service:

\begin{itemize}
\item Qual committee (writing, grading, both quals in 2018)
\item Web committee (Chair)
\item Saturday Morning Physics
\end{itemize}



\newpage

\noindent B. PAPERS PUBLISHED THIS YEAR. Please list by citation all
papers of which you were an author that appeared during 2018.
(Designate whether refereed, conference proceeding, abstract etc.)

\begin{itemize}
\item
``Near-infrared Spectral Evolution of the Type Ia Supernova 2014J in the Nebular
Phase: Implications for the Progenitor System''
Diamond, T. R.; Hoeflich, P.; Hsiao, E. Y.; Sand, D. J.; Sonneborn, G.;
Phillips, M. M.; Hristov, B.; Collins, D. C.; Ashall, C.; Marion, G. H.;
Stritzinger, M.; Morrell, N.; Gerardy, C. L.; Penney, R. B.
ApJ, 2018, 861, 119
\item
``Magnetohydrodynamical Effects on Nuclear Deflagration Fronts in Type Ia Supernovae''
Hristov, Boyan; Collins, David C.; Hoeflich, Peter; Weatherford, Charles A.; Diamond, Tiara R., 
ApJ, 2018, 858, 13
\item 
``The Anatomy of the Column Density Probability Distrbution Function (N-PDF)''
Chen, H., Burkhart, B., Goodman, A. A., Collins, D. C. 
ApJ, 2018, 859, 162
\end{itemize}


\noindent C. PAPERS IN PRESS. Please list by citation all such
papers that were accepted but did not appear during 2018.


\noindent D. PAPERS SUBMITTED. Please list all papers that were
submitted by you but were not yet accepted during 2018.

\begin{itemize}
    \item
``The Impact of Enhanced Halo Resolution on the Simulated Circumgalactic Medium''
Hummels, Cameron B.; Smith, Britton D.; Hopkins, Philip F.; O'Shea, Brian W.; Silvia, Devin W.; 
Werk, Jessica K.; Lehner, Nicolas; Wise, John H.; Collins, David C.; Butsky, Iryna S.   
\emph{Submitted} Arxiv 18111241, 2018
\end{itemize}


\noindent E. INDIVIDUAL TALKS. Please list all conference, symposia,
colloquia, seminar and other individual talks that you gave during
2018.  (Designate invited talks.)

\begin{itemize}
\item
``Turbulent Space Magnets'', FSU Physics Colloquium
Sept. 6, 2018

\item
``Black Holes!'' Quarknet 2018, FSU, July 21 2018.

\item
``How to Break Enzo'' Enzo New Users Workshop, Georgia Tech University, May 8
2018

\item
``Astrophysical Turbulence with Magnetic Fields'' Emory University Physics
Colloquium, April 17 2018

\item
``What’s the Deal with Dark Matter?'' FSU, {\it Society of Physics Students},
March 6, 2018
\end{itemize}


%

\noindent F. GRANT FUNDING. Please indicate your research funding
for 2018. Include any submitted  (even if not funded) or pending
proposals.
%\bigskip
%
\noindent\emph{FUNDED}

\begin{itemize}
    \item Peter Hoeflich (PI) Eric Hsiao (Co-PI) David Collins (Co-PI)
``Signatures of Type Ia Supernovae Explosions and their Cosmological
Implications`` August 2017-August 2020. NSF, \$421,215 over 3 years

\item Collins, David C. (Co-PI), \& Huffenberger, Kevin (PI). (Feb 2017–Feb 2020).
``Modeling CMB Polarization Foregrounds and their Isotropy Violation.'' Funded
by National Aeronautics \& Space Administration. (NNX17AF87G). \$428,043 over 3
years

\item Collins, David C. (PI). (Sep 2016–Aug 2019). ``A Study of Magnetic Fields
in the Formation of Molecular Clouds and Stars.'' Funded by National
Science Foundation. (1616026). Total award \$198,250.00 over 3 years

\item ``Tracking the Assembly History of Star Formation through Clouds, Filaments, and
Cores: Phase I.'' XSEDE computational resources.  Awarded 1.6 million CPU hours,
in kind value of \$50,000
\end{itemize}

\noindent\emph{PENDING}

\emph{nothing pending}

\noindent G. DEPARTMENTAL COMMITTEE SERVICE. Please list all
departmental committees on which you served during 2018.  Also
please indicate your committee assignment for this (spring)
semester.
%
\begin{itemize}
\item Qual committee (writing, grading, proctoring both quals in 2018)
\item Web committee (Chair)
\item Saturday Morning Physics
\item These will stay the same Spring 2019.
\end{itemize}

\noindent H. UNIVERSITY AND SUS SERVICE. Please list all University
and SUS committees, task forces, and governing bodies on which you
served during 2018.
\bigskip
%

\noindent I. INTERNATIONAL, NATIONAL, AND REGIONAL  SERVICE. Please
list all international, national, and regional bodies on which you
served, together with any reviewing activities (journals,
proposals), during 2018.

\begin{itemize}
    \item Continued support and development of the open-source community
        astrophysics simulation software, Enzo.  
\end{itemize}

\noindent J. OFFICES HELD. Please list all offices in organizations
related to your activity as a professional faculty member held by
you during 2018.
\bigskip

\noindent K. HONORS RECEIVED. Please list all professional honors
received by you during 2018.
\bigskip

\noindent L. GRADUATE DEGREES AWARDED. Please list all graduate
students who received degrees under your direction during 2018.
\bigskip

\begin{itemize}
    \item Boyan Hristov, jointly advised FAMU PhD student.
\end{itemize}

\noindent M. GRADUATE STUDENT DIRECTION. Please list all graduate
students whose work you directed during 2018 but who did not receive
degrees.

\begin{itemize}
    \item I continued advising the PhD of Dan K. Le, Kye Stalpes, 
    \item Luz Jimenez transitioned from Masters to PhD student.
\end{itemize}

\noindent N. GRADUATE STUDENT COMMITTEES. Please list all graduate
students on whose supervisory committees you served but for whom you
were not Major Professor during 2018.

\begin{itemize}
    \item Vincent Lakey, Brittany Fuzia, Quintin Mabanta, Alec Fisher, Erica
Bloor, Carlos Garcia, Kuan-Wen Chen.
\end{itemize}

\noindent O. UNDERGRADUATE SUPERVISION. Please list all
undergraduate students whose research activities you directed during
2018.

\begin{enumerate}
    \item Fabio Rivero.
    \item Dakota Bosch
    \item Douglas Schoedel
\end{enumerate}

\noindent P. CLASSES TAUGHT. Please list all classes you taught
during 2018 and what you are teaching this semester.  Include the
number of students in each class.

\begin{itemize}
\item 4419/5418, Extragalactic Astronomy ( Spring 2018) 
\item AST 5219/AST 4218 Astro Seminar (Spring)
\item AST-4341/AST-5342, Hydrodynamcis for Astrophysics (Fall)
\end{itemize}


\noindent Q. DIS SUPERVISION. Please list all DIS (Directed
Individual Study) students you directed during 2018.

\begin{itemize}
    \item Dan Le
    \item Luz Jiminez
    \item Kye Stalpes
\end{itemize}

\noindent R. OUTREACH ACTIVITIES. Please list all outreach
activities that you have participated in during 2018.

\begin{itemize}
    \item Ask A Scientist
    \item Saturday Morning Physics
    \item Talk at Quarknet
\end{itemize}

\noindent S. OTHER ITEMS. Please detail any other items that you
feel will help give an adequate picture of your performance during
2018.
\bigskip

\noindent T.  SPCI EVALUATIONS. Please attach a copy of all student
evaluation SPCI form summary pages for your teaching during 2018.


\end{document}



