\documentstyle[12pt]{article}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{2.5cm}
\addtolength{\oddsidemargin}{-.75in}
\addtolength{\evensidemargin}{-.75in}
\addtolength{\textwidth}{.5in}
\begin{document}

%\vskip 1 in
\centerline{EVIDENCE OF PERFORMANCE}
%\centerline{(compressed format)}
\bigskip
\centerline{YEAR: \underbar{2021}}
\bigskip
\noindent Name: \underbar {David C. Collins }
\hbox{\ \ \ \ \ \ \ \
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ }
Rank: \underbar
{Associate Professor }

%\bigskip
\vskip 20pt

\noindent A. YOUR MOST SIGNIFICANT CONTRIBUTIONS FOR THIS YEAR.
Please select from this document what you consider were your most
significant contributions (i.e. bragging points) in each of the areas of teaching, research
and service. PLEASE LIST THEM IN BULLET FORM AND ICLUDE A BRIEF 
DESCRIPTION AND/OR SUPPORTIVE INFORMATION AS SUB-BULLETS. 
If there is something important that you would like to mention which
lies outside these categories, please
place it in a category named ``Other'' at the bottom of this page. \\ \\

To assist in evaluating faculty accomplishments, faculty may include pandemic impact statements in their evidence of performance reports.  \textbf {Additional detail and guidance is provided in the University Memorandum on the Guidelines for 2021 \textit{Annual Performance Evaluations}.}


\vskip 10pt
\noindent
Teaching:
\begin{itemize}
	\item AST-4419/AST-5418 Extragalactic Astronomy (Spring 2021)
	\item 2053 Recitation (Fall 2021)
	\item Four PhD students, one undergraduate, one postdoc, 
    \item Departmental advisor for one PhD student in
        Engineering.
\end{itemize}
\vskip 30pt

\noindent
Research:
\begin{itemize}
	\item Star Formation: Four papers forthcoming.  Grant supported.
        \begin{enumerate}
            \item Luz Jimenez Vela and Dan Le are working on this.
            \item We have simulated clouds of gas collapsing under their own
                gravity to understand how stars form.          \end{enumerate}
	\item Supernovae: One paper published.   Grant supported.
        \begin{enumerate}
            \item Boyan Hristov was working on this.
            \item We have simulated exploding white dwarf stars with magnetic
                fields.  We have shown that large magnetic fields are necessary
                to reproduce observed decline in brightness over several hundred
                days of Type Ia Supernovae.
        \end{enumerate}
	\item CMB Foregrounds: One paper forthcoming.  Grant supported.
        \begin{enumerate}
            \item Kye Stalpes is on this.
            \item Seeing the impact of inflation on the CMB requires
                understanding the polarized light from the galaxy that is in the
                way.  This work explores the polarization of magnetized
                turbulence to understand the interstellar medium
            \item One proposal submitted (rejected) to NASA.
        \end{enumerate}
    \item Star Formation with the National Ignition Facility: Shots July 13th
        2022.
        Two papers submitted.  
        \begin{enumerate}
            \item Luz Jimenez Vela is working on this.
            \item My entry into experimental physics!  We have been awarded two
                shot days (July 13, 2022 and undetermined date in 2023) at the
                National Ignition Facility, which houses the most powerful laser
                in the world, to experimentally validate an important relation that
                is used in star formation theory.
        \end{enumerate}
    \item Galactic Magnetic Fields.  
        \begin{enumerate}
            \item Jacob Strack is working on this.
            \item We are simulating the growth of the magnetic field in the
                galaxy.  
            \item One proposal submitted to NSF to support Galactic Magnetic
                Fields (pending, very promising)
        \end{enumerate}
\end{itemize}
\vskip 30pt

\noindent
Service:
\begin{itemize}
	\item Qual Committee 
        \begin{enumerate}
            \item Writing and grading both exams
            \item Planning the future of the exam in the department
        \end{enumerate}
	\item Web committee (chair)
        \begin{enumerate}
            \item Organize the maintenance and upkeep of the department
                website.
            \item Ensure the website is attractive and useful for current
                and prospective students, staff, and faculty.
        \end{enumerate}
	\item Saturday Morning Physics
        \begin{enumerate}
            \item Presentations about astronomy to area middle school students.
                Reaches about 150 students.
        \end{enumerate}
    \item PAI committee (chair)
        \begin{enumerate}
            \item Organize collecting nominations and selecting of the winner of
                the annual PAI award for faculty members.
        \end{enumerate}
\end{itemize}	
\vskip 30pt



\noindent B. PAPERS PUBLISHED THIS YEAR. Please list by citation all
papers of which you were an author that appeared during 2021.
(Designate whether refereed, conference proceeding, abstract etc.)
\bigskip

\begin{itemize}
    \item ``Physics of Thermonuclear Explosions: Magnetic Field Effects on
        Deflagration
        Fronts and Observable Consequences'', Hristov, Boyan; Hoeflich, Peter;
        Collins,
        David C., ApJ, 2021, 923, 210, 21
    \item
``Measuring an Off-center Detonation through Infrared Line Profiles: The
Peculiar Type Ia Supernova SN 2020qxp/ASASSN-20jq'' P. Hoeflich, C. Ashall,
S. Bose , E. Baron , M. D. Stritzinger , S. Davis , M. Shahbandeh , G. S.
Anand ,
D. Baade , C. R. Burns , D. C. Collins , T. R. Diamond , A. Fisher , L.
Galbany , B. A. Hristov ,
E. Y. Hsiao, M. M. Phillips, B. Shappee, N. B. Suntzeff, and M.
Tucker.  ApJ, 2021, 922, 2, 21
\end{itemize}


\noindent C. PAPERS IN PRESS. Please list by citation all such
papers that were accepted but did not appear during 2021.
\bigskip

\begin{itemize}
    \item 
        ``The driving mode of shock-driven turbulence'',
        Saee Dhawalikar, Christoph Federrath, Seth Davidovits, Romain
        Teyssier, Sabrina R. Nagel, Bruce A. Remington, and David C. Collins
        (Submitted to Monthly Notices of the Royal Astronomical Society)
    \item
        ``Turbulence generation by shock interaction with a highly non-uniform
        medium'', Seth Davidovits, Christoph Federrath, Romain Teyssier,
        Kumar S. Raman, David C. Collins, and Sabrina R. Nagel  (submitted to
        Physical
        Review E)
\end{itemize}

\noindent D. PAPERS SUBMITTED. Please list all papers that were
submitted by you but were not yet accepted during 2021.
\bigskip


\noindent E. INDIVIDUAL TALKS. Please list all conference, symposia,
colloquia, seminar and other individual talks that you gave during
2021.  (Designate invited talks.)
\bigskip
%
\begin{itemize}
    \item ``Letting Anxiety Work For You: Lessons from Outer Space'' Highway
        Safety Toastmasters, 2021-09-27
\end{itemize}

\noindent F. GRANT FUNDING. Please indicate your research funding
for 2021. Include any submitted  (even if not funded) or pending
proposals.   {\bf Include the FSU Project Number.}
\bigskip
%

\begin{itemize}
    \item ``Signatures of Type Ia Supernovae Explosions and their Cosmological
        Implications'' NSF AAG, (current) \$421,215 10/1/2017-9/21/2022
    \item ``CMB Polarization Foreground Effects on B-modes and Lensing'' NSF
        AAG, (current) \$533,715 8/1/2020-7/31/2023
    \item ``Modeling CMB polarization foregrounds and their isotropy violation''
        NASA (current) \$421,215 1/8/2017-2/2/22
    \item ``A Study of Magnetic Fields in the Formation of Molecular Clouds and
        Stars'' NSF AAG (current) \$298,420 9/1/2016-8/31/2022
    \item ``Laser Experiements on the Turbulent Formation of Stars'', two shot
        days awarded at the National Ignition Facility for FY2022 and FY2023.
    \item ``Collaborative research: Galactic and circumgalactic magnetic fields
        in Milky Way-like galaxies'' NSF AAG (pending) \$425,000
\end{itemize}

\noindent G. DEPARTMENTAL COMMITTEE SERVICE. Please list all
departmental committees on which you served during 2021.  Also
please indicate your committee assignment for this (spring)
semester.
\bigskip
%
\begin{itemize}
    \item Qual Committee
    \item Web Committee (chair)
    \item PAI Committee (chair)
    \item Saturday Morning Physics
\end{itemize}

\noindent H. UNIVERSITY AND SUS SERVICE. Please list all University
and SUS committees, task forces, and governing bodies on which you
served during 2021.
\bigskip
%

\noindent I. INTERNATIONAL, NATIONAL, AND REGIONAL  SERVICE. Please
list all international, national, and regional bodies on which you
served, together with any reviewing activities (journals,
proposals), during 2021.
\bigskip

\begin{itemize}
    \item Support and development for the open-source community astrophysics
        simulation software, Enzo.
    \item NASA Astrophysics Theory proposal panel review
    \item Refereed papers for astrophysics journals.
\end{itemize}

\noindent J. OFFICES HELD. Please list all offices in organizations
related to your activity as a professional faculty member held by
you during 2021.
\bigskip

\noindent K. HONORS RECEIVED. Please list all professional honors
received by you during 2021.
\bigskip

\noindent L. GRADUATE DEGREES AWARDED. Please list all graduate
students who received degrees under your direction during 2021.
\bigskip

\noindent M. GRADUATE STUDENT DIRECTION. Please list all graduate
students whose work you directed during 2021 but who did not receive
degrees. {\bf Include date joined group, prospectus (expected/passed) date, 
and expected graduation date.}
\bigskip

\begin{enumerate}
    \item Dan Le.  Joined Jan 2015.  Prospectus Dec 2019.   Graduation Summer
        2022.
    \item Kye Stalpes.  Joined Jan 2016.  Prospectus Dec 2019.  Graduation
        Summer 2022.
    \item Luz Jimenez Vela.  Joined July 2016 via the Bridge program.
        Prospectus TBD, Spring 2022.  Expected graduation 2025.
    \item Brano Rabatin.  Joined Spring 2019.  Prospectus TBD, Spring 2022.
        Expected graduation 2025.
    \item Toshiaki Kanai.  Major Professor is Wei Guo in Engineering.  Joined
        Fall 2020.  Prospectus March 2021.  
\end{enumerate}

\noindent N. GRADUATE STUDENT COMMITTEES. Please list all graduate
students on whose supervisory committees you served but for whom you
were not Major Professor during 2021. {\bf Include name of Major Professor 
and department if outside of Physics. }
\bigskip

\begin{enumerate}
    \item Alec Fisher
    \item Carlos Garcia 
    \item Erica Bloor
    \item Erica Knorr (Chemistry, Ken Hanson)
    \item Yavuz Oz
    \item Paudel Nawaraj
    \item Shu Liu
\end{enumerate}

\noindent O. UNDERGRADUATE SUPERVISION. Please list all
undergraduate students whose research activities you directed during
2021.  {\bf Include a research title or brief description. }
\bigskip

\begin{enumerate}
    \item Douglas Schoedel.  Properties of the Interstellar Medium.
\end{enumerate}

\noindent P. CLASSES TAUGHT. Please list all classes you taught
during 2021 and what you are teaching this semester.  Include the
number of students in each class.
\bigskip


\begin{itemize}
	\item AST-4419/AST-5418 Extragalactic Astronomy (Spring 2021)
	\item 2053 Recitation (Fall 2021)
\end{itemize}

\noindent Q. DIS SUPERVISION. Please list all DIS (Directed
Individual Study) students you directed during 2021.
\bigskip

\begin{itemize}
    \item Morgan Adams
    \item Luz Jimenez Vela
    \item Brano Rabatin
\end{itemize}

\noindent R. {\bf POSTDOCTORAL SCHOLAR SUPERVISION}. Please list all postdoctoral scholars whose work you directed during 2021.  {\bf Include name, date joined group, residency}(i.e. PHYSICS, MAGLAB, CERN, POINT NEMO){\bf, and current status. }
\bigskip

\begin{itemize}
    \item Boyan Hristov
\end{itemize}


\noindent S. OUTREACH ACTIVITIES. Please list all outreach
activities that you have participated in during 2021.
\bigskip

\begin{itemize}
    \item Ask A Scientist (Organizer); Monthly public event where people can ask questions
        of professional scientists.  Covid disrupted activities for 2021, but
        will resume in 2022.
    \item Saturday Morning Physics
    \item Toastmasters; I participated in a Toastmasters event, where I
        presented my experience working around anxiety when giving talks.
\end{itemize}

\noindent T. OTHER ITEMS. Please detail any other items that you
feel will help give an adequate picture of your performance during
2021.
\bigskip

\noindent U.  SPCI EVALUATIONS. Please attach a copy of all student
evaluation SPCI form summary pages for your teaching during 2021.


\end{document}


 
