
\documentclass[10pt]{article}
\topmargin -.5in
\textwidth 6.5in
\textheight 9in
\oddsidemargin 0in

\pagestyle{empty}

\begin{document}
\begin{center}
\noindent{\bf\large RESEARCH TIMELINE}\end{center}
\begin{center}{\bf 2001}\end{center}

\noindent\rule[3pt]{\textwidth}{.1mm}

\noindent\rule[3pt]{\textwidth}{.1mm}


\noindent\rule[3pt]{\textwidth}{.1mm}

Took classes.

\noindent{\bf Fall} Began graduate school.

\noindent{\bf October} Asked Maggie to move out.

\begin{center}{\bf 2002}\end{center}

\noindent\rule[3pt]{\textwidth}{.1mm}

More classes.

\noindent{\bf Summer} Maggie moves out.  Study for the Qual with Daniel Queen.

\noindent{\bf Fall} Pass Qual.  Quit smoking.

\noindent{\bf December} Start talking to Mike Norman.

\begin{center}{\bf 2003}\end{center}

\noindent\rule[3pt]{\textwidth}{.1mm}

More classes.

\noindent{\bf Winter} Planet formation papers.

\noindent{\bf Spring} Start working with Paolo.

\noindent{\bf Summer} Start reading for MHD Enzo.

Also working with Pak Shing on a $1024^3$ on Lemieux that failed.

\noindent{\bf December} Stared \emph{Book I}: broke Enzo ground.

\begin{center}{\bf 2004}\end{center}

\noindent\rule[3pt]{\textwidth}{.1mm}

Major Enzo development.  Had all major parts in and finished by December.
\emph{Book I - Book IV} filled, \emph{Book V} started.  
Paolo turbulence?  Diamond turbulence?

\noindent{\bf December 16-23} Copenhagen trip. Start \emph{Book V} with re-hashing AMR machinery.



\begin{center}{\bf 2005}\end{center}

\noindent\rule[3pt]{\textwidth}{.1mm}

\noindent{\bf January} AAS meeting.  O'Shea moves.  

\noindent{\bf Winter?} Debugging $\nabla \cdot B$.  Reading numerical papers. Start \emph{Book VI} somewhere in here.  (Might have been
concurrent with \emph{Book V}: \emph{Book VI} is mostly notes on papers)

\noindent{\bf March} IPAM workshop.  Acceleration Boundary.

\noindent{\bf Spring} SUBling fix.  Somewhere in here started \emph{Book VII}

\noindent{\bf May 30} Got Married.

At this point I quite wish I had dated my notebooks.

\noindent{\bf June 28-July 17} Dublin/Cambridge (was definitely working on SUBling at a
cafe in Cambridge.)

\noindent{\bf 7/7}

\noindent{\bf September 19} Dates appear in \emph{Book VI}!  (God, this one is pretty
useless.  It has the details of finding bugs, but no bug description, no notes
or successes.)

tracking down divergence; getting Flux Correction right (pre E projection? Can't
tell what notes these are. \emph{Book VII}

\noindent{\bf September 24} Start the CVS repository.

\noindent{\bf October} Hao joins the project.  Still debugging SUBling, it seems.  

\noindent{\bf October 24-28} Protostars and Planets V.


\noindent{\bf Fall-Winter} Quagmire.  No focus, stuck on code garbage.  Needed guidance.
Sibling-SUBling attempts, failures.  

\noindent{\bf November} Start \emph{Book VIII}.  Seems to have much better notes.

\noindent{\bf December} 'Waffle Instability'.  KH and driven turbulence.  (I think this
is even-odd in Balsara CT.)

\begin{center}{\bf 2006}\end{center}

\noindent\rule[3pt]{\textwidth}{.1mm}

\noindent{\bf January} Balsara higher order centering.  (Not really worth the code updates
necessary.)

\noindent{\bf April 25-30} Visit Los Alamos.  Start an Enzo method paper that didn't
materialize.  Mike suggests Davethena.

\noindent{\bf May, June.} Learning about writing a solver.  

\noindent{\bf June 21 - July 2 } Warwick meeting.

\noindent{\bf July-August} Athena Electric code.

\noindent{\bf September} Flattening, Diffusion, fail check.

\noindent{\bf October} Riemann solvers.  Start \emph{Book IX}. The beginning of driving
problems.  (Curse)

\emph{Book IX} is great.

\noindent{\bf November, December} More driving problems. Checkerboard detector, oblique
shocks.  Notes on AMR + Stagger.  Relatively unproductive. 


\begin{center}{\bf 2007}\end{center}

\noindent\rule[3pt]{\textwidth}{.1mm}

\noindent{\bf January} More driving problems.  

\noindent{\bf February} Shifted boundary conditions for oblique shocks.  Gravity in Ryu and Jones (Why?)
Solver notes from Laney.

\noindent{\bf March} Re-discovering the inconsistencies of gravity.  Good notes on
gravity solver.  Ran one successful collapse, but there was only one object,
collapse stalled, as did my focus and direction.

Seriously, what the hell was I doing here?

\noindent{\bf April} Maggie gets a new job.  Saltzmann viscosity.  PPML

\noindent{\bf May} PPML?

\noindent{\bf June} Reading PPM paper.  Paolo's sticking sphere (he had moved on to
Ramses by this point)

\noindent{\bf June 30-July 16} Helsinki

\noindent{\bf July 26-29} Comic-Con with Patrick.  Vierra.

\noindent{\bf August 3 ish} trip home.  Mike: "Wow, your code sucks more than SPH."

\noindent{\bf August 13-17} Santa Barbara workshop. Vierra's memorial.

\noindent{\bf October, November} In Santa Barbara.  Running comparisons between Dave
Thena (now stable) and PPML (now with crazy even-odd).

\emph{Could use more detail, this is from memory.}

\noindent{\bf Dec} KITP initial conditions kill PPML, Dave Thena.

\begin{center}{\bf 2008}\end{center}

\noindent\rule[3pt]{\textwidth}{.1mm}

\noindent{\bf Winter} Dispair.  

\noindent{\bf Spring} Start using Li \& Li (dates?)

\noindent{\bf Summer} Unsure what was going on here.

\noindent{\bf Fall} Method paper.  Try to get something to graduate with.

\begin{center}{\bf 2009}\end{center}

\noindent\rule[3pt]{\textwidth}{.1mm}

\noindent{\bf January} AAS in Long Beach.  Start running sims.  Find bug with gravity.

\noindent{\bf February} Run new sims (Virial Parameter Suite), write like a mad bitch.

\noindent{\bf March} More thesis writing.  Now we're productive.

\noindent{\bf April} Defend Thesis!  Max arrives!

\noindent{\bf May} Nothing.

\noindent{\bf Summer} Week of Code. Code merger. Tracking down $\nabla \cdot B$ for Method paper.  Find
stalled core bug, exploding filiament bug in new simulations.  Run scaling study
(take 1.)  Shetty paper work.

\noindent{\bf Fall} ... Clump tracker started, I'm sure there was something else here.

\noindent{\bf Winter} kind of useless, I think.  Clump tracker, maybe.  Looking at plots.

\begin{center}{\bf 2010}\end{center}

\noindent\rule[3pt]{\textwidth}{.1mm}

\noindent{\bf Winter} Too much clump tracker.  Alpha study.  Can alpha study.

\noindent{\bf Spring} Scaling study.  Gainsville meeting.  Poster.

\noindent{\bf Summer} Enzo Workshop, two presentations.  Malinen paper submitted.
Stanford study started, stanford visit.  Paper2.5 submitted, accepted.

\noindent{\bf Fall}  Started Multiphase.  Installed cooling.  HLLD sucking.  Finished
Paper2.5 revisions, but unsure what to do with what I wrote.  Began Beta
variation study.




\end{document}
