\documentstyle[12pt]{article}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{2.5cm}
\addtolength{\oddsidemargin}{-.75in}
\addtolength{\evensidemargin}{-.75in}
\addtolength{\textwidth}{.5in}
\begin{document}

%\vskip 1 in
\centerline{EVIDENCE OF PERFORMANCE}
%\centerline{(compressed format)}
\bigskip
\centerline{YEAR: \underbar{2019}}
\bigskip
\noindent Name: \underbar {David C. Collins}
\hbox{\ \ \ \ \ \ \ \
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ }
Rank: \underbar
{ }

%\bigskip
\vskip 20pt

\noindent A. YOUR MOST SIGNIFICANT CONTRIBUTIONS FOR THIS YEAR.
Please select from this document what you consider were your most
significant contributions in each of the areas of teaching, research
and service. PLEASE LIST THEM IN BULLET FORM AND ICLUDE A BRIEF 
DESCRIPTION AND/OR SUPPORTIVE INFORMATION AS SUB-BULLETS. 
If there is something important that you would like to mention which
lies outside these categories, please
place it in a category named ``Other'' at the bottom of this page. \\ \\

\noindent
Teaching:

\begin{itemize}
\item AST-4419/AST 5418, Extragalactic Astronomy (Spring) 
\item AST-4341/AST-5342, Hydrodynamcis for Astrophysics (Fall)
\item Four PhD students, two undergraduate, one postdoc.
\end{itemize}

\noindent
Research:

\begin{itemize}
    \item One paper accepted, one submitted
    \item Two  presentations
    \item Several grant proposals
\end{itemize}

\noindent
Service:

\begin{itemize}
\item Qual committee (writing, grading, both quals in 2019)
\item Web committee (Chair)
\item Saturday Morning Physics
\item PAI committee
\end{itemize}

\newpage

\noindent B. PAPERS PUBLISHED THIS YEAR. Please list by citation all
papers of which you were an author that appeared during 2019.
(Designate whether refereed, conference proceeding, abstract etc.)
\bigskip

\begin{itemize}
    \item
``The Impact of Enhanced Halo Resolution on the Simulated Circumgalactic Medium''
Hummels, Cameron B.; Smith, Britton D.; Hopkins, Philip F.; O'Shea, Brian W.; Silvia, Devin W.; 
Werk, Jessica K.; Lehner, Nicolas; Wise, John H.; Collins, David C.; Butsky, Iryna S.   
ApJ 2019, 882, 156 
\end{itemize}


\noindent C. PAPERS IN PRESS. Please list by citation all such
papers that were accepted but did not appear during 2019.
\bigskip


\noindent D. PAPERS SUBMITTED. Please list all papers that were
submitted by you but were not yet accepted during 2019.
\bigskip
\begin{itemize}
    \item ``The Power Spectra of Polarized, Dusty Filaments'', Huffenberger, K.;
        Rotti,
        A., Collins, D. C., Submitted to ApJ, ArXiv 2019arXiv190610052H
\end{itemize}


\noindent E. INDIVIDUAL TALKS. Please list all conference, symposia,
colloquia, seminar and other individual talks that you gave during
2019.  (Designate invited talks.)
\bigskip

\begin{itemize}
    \item ``Interpreting CMB Foregrounds,'' \emph{Big Apple Magnetic Fields},
        Flatiron Institute for Computational Astrophysics Jan 25, 2019
    \item ``Turbulent Space Magnetic,'' FSU Department of Scientific Computing,
        Feb 2, 2020.
\end{itemize}

\noindent F. GRANT FUNDING. Please indicate your research funding
for 2019. Include any submitted  (even if not funded) or pending
proposals.   Include the FSU Project \#.
\bigskip
%

\textbf{Funded}
\begin{enumerate}
    \item ``Magnetic Fields in the Formation of Molecular Clouds,
Filaments, and Cores''.  NSF AAG. FSU id 037693.  \$298,492 09/01/2016 - 08/31/2019
\item  ``Modeling CMB polarization foregrounds and their isotropy violation''
    NASA ATP.  01/08/2017 - 01/07/2020  \$428,043.00
\item ``Signatures of Type Ia Supernovae Explosions and their Cosmological
    Implications'' NSF AAG FSU id 039518 10/01/2017 - 09/31/2020 \$460,498
\end{enumerate}


\textbf{Rejected or Pending Rejection}
\begin{enumerate}
\item ``Unravelling the Radio Sky: Synchrotron Emission and the Extragalactic
    Radio Background'' NASA ADAP \$498,000 (rejected)
\item ``Laser Experiements on the Turbulent Formation of Stars'' National
    Ignition Facility shot proposal (rejected)
\item ``Simulating CMB Foregrounds'' NASA ATP \$510,000 (rejected)
\item ``SNE Ia: Imprints of the Explosion \& Projenitor, Model-Independent
    Relations \& Cosmology'' NSF AAG \$498,000(pending)
\item ``Simulating Cosmic Magnetism'' NSF AAG \$282,000 (pending) 
\item ``CMB Polarization Foreground Effects on B-modes and Lensing'' NSF AAG
    \$533,000 (pending)
\item ``Mitigating Galactic Foreground Contamination for CMB-S4 Lensing and
    Delensing'' DOE \$683,000 (pending)
\end{enumerate}

\noindent G. DEPARTMENTAL COMMITTEE SERVICE. Please list all
departmental committees on which you served during 2019.  Also
please indicate your committee assignment for this (spring)
semester.
\bigskip
%

Both 2019 and Spring 2020
\begin{itemize}
\item Qual committee (writing, grading, proctoring both quals in 2019)
\item Web committee (Chair)
\item Saturday Morning Physics
\item PAI committee (Chair)
\end{itemize}

\noindent H. UNIVERSITY AND SUS SERVICE. Please list all University
and SUS committees, task forces, and governing bodies on which you
served during 2019.
\bigskip
%

\noindent I. INTERNATIONAL, NATIONAL, AND REGIONAL  SERVICE. Please
list all international, national, and regional bodies on which you
served, together with any reviewing activities (journals,
proposals), during 2019.
\bigskip

\begin{itemize}
    \item Continued support and development of the open-source community
        astrophysics simulation software, Enzo.  
    \item NASA Astrophysics Theory proposal review panel
    \item Refereed papers
\end{itemize}

\noindent J. OFFICES HELD. Please list all offices in organizations
related to your activity as a professional faculty member held by
you during 2019.
\bigskip

\noindent K. HONORS RECEIVED. Please list all professional honors
received by you during 2019.
\bigskip

\noindent L. GRADUATE DEGREES AWARDED. Please list all graduate
students who received degrees under your direction during 2019.
\bigskip

\noindent M. GRADUATE STUDENT DIRECTION. Please list all graduate
students whose work you directed during 2019 but who did not receive
degrees. Include date joined group, prospectus (expected/passed) date, 
and expected graduation date.
\bigskip
\begin{enumerate}
    \item Dan Le.  Prospectus Dec 2019.  Joined Jan 2015.  Expected graduation
        early 2021.
    \item Kye Stalpes.  Prospectus Dec 2019.  Joined Jan 2016.  Expected
        graduation late 2021
    \item Luz Jimenez.  Pre-qual.  Joined July 2016 as a Master's student.
        Expected graduation 2024.
    \item Bra\u{n}o Rabatin.  Pre-prospectus.  Joined Spring 2019.  Expected
        graduation 2025.
\end{enumerate}

\noindent N. GRADUATE STUDENT COMMITTEES. Please list all graduate
students on whose supervisory committees you served but for whom you
were not Major Professor during 2019.  Include name of Major Professor 
and department if outside of Physics.
\bigskip

\begin{enumerate}
    \item Bloor, Erica
    \item Garcia, Carlos
    \item Knorr, Erica (Chemistry, Ken Hanson)
    \item Lakey, Vincent
    \item Mabanta, Quntin
    \item Oz, Yavuz
    \item Rosales, Daniel (GFDI/Scientific Computing.  Kevin Speer)
\end{enumerate}

\noindent O. UNDERGRADUATE SUPERVISION. Please list all
undergraduate students whose research activities you directed during
2019.  Include a research title or brief description.
\bigskip

\begin{enumerate}
    \item Schoedel, Douglas.  ``Simulations of Thermally Unstable Gas for CMB
        Foreground Decontamination.''
    \item Bosch, Dakota.  Performed simulations of MHD wave advection for use in
        CMB foreground studies.
\end{enumerate}

\noindent P. CLASSES TAUGHT. Please list all classes you taught
during 2019 and what you are teaching this semester.  Include the
number of students in each class.
\bigskip

\begin{itemize}
\item AST-4419/AST 5418, Extragalactic Astronomy (Spring 2020, 10 students) 
\item AST-4341/AST-5342, Hydrodynamcis for Astrophysics (Fall 2019, 8 students)
\item AST-4419/AST 5418, Extragalactic Astronomy (Spring 2019, 8 students) 
\end{itemize}

\noindent Q. DIS SUPERVISION. Please list all DIS (Directed
Individual Study) students you directed during 2019.
\bigskip

\begin{itemize}
    \item Dan Le
    \item Luz Jimenez
    \item Kye Stalpes
    \item Bra\u{n}o Rabatin
    \item Doug Schoedel
\end{itemize}

\noindent R. OUTREACH ACTIVITIES. Please list all outreach
activities that you have participated in during 2019.
\bigskip

\begin{itemize}
    \item Ask A Scientist (Organizer, roughly monthly)
    \item Saturday Morning Physics
\end{itemize}

\noindent S. OTHER ITEMS. Please detail any other items that you
feel will help give an adequate picture of your performance during
2019.
\bigskip

\noindent T.  SPCI EVALUATIONS. Please attach a copy of all student
evaluation SPCI form summary pages for your teaching during 2019.


\end{document}



